The Types and Driving Forces of Modifications in the Evolution of an API

### 2015-05-12 thesis/paper.tex
Fixed typo preventing compilation

\smallskip \noindent
\textbf{Adaptive  }
No adaptive changes were found

>>>>

\smallskip \noindent
\textbf{Adaptive  }
%Introduction and definition
Adaptive changes are defined to be changes which involve changes to technology or resources used. 
%Data and examples
A single change was identified as being adaptive; the inclusion of new 3\textit{rd} part libraries. Glib existed in version 1.4 of the API its use was increased in version 2.0. Furthermore, other libraries were added for audio and data communication.

This type of change made up 7.7\% of the total changes, however it had a broader impact than other individual changes.

%Conclusion
